\begin{tcolorbox}[colback=white, colframe=gray!60, title=Remark 1]
A \textbf{truth table} can be used to determine whether a compound proposition is \textbf{satisfiable}, or
equivalently, whether its negation is a tautology (see \textbf{Exercise 64}). \newline
This can be done by
hand for a compound proposition with a small number of variables, but when the number
of variables grows, this becomes impractical.
\end{tcolorbox}
\begin{tcolorbox}[colback=white, colframe=gray!60, title=Remark 2]
\textbf{Because the problem scales as $2^n$, where $n$ is the number of variables.} \newline
For instance, there are $2^{20} = 1,048,576 \ \text{rows}$
in the truth table for a compound proposition with 20 variables. Thus, you need a computer
to help you determine, in this way, whether a compound proposition in 20 variables is
satisfiable.
\end{tcolorbox}
\begin{tcolorbox}[colback=white, colframe=gray!60, title=Remark 3]
When many applications are modeled, questions concerning the satisfiability of compound
propositions with hundreds, thousands, or millions of variables arise. Note, for example, that
when there are 1000 variables, checking every one of the $2^{1000}$ (a number with more than 300
decimal digits) possible combinations of truth values of the variables in a compound proposition
cannot be done by a computer in even trillions of years
\end{tcolorbox}
\begin{tcolorbox}[colback=white, colframe=gray!60, title=Remark 4]
No procedure is known that a computer
can follow to determine in a reasonable amount of time whether an arbitrary compound
proposition in such a large number of variables is satisfiable. However, progress has been made
developing methods for solving the satisfiability problem for the particular types of compound
propositions that arise in practical applications, such as for the solution of Sudoku puzzles.
\end{tcolorbox}
\begin{tcolorbox}[colback=white, colframe=gray!60, title=Remark 5]
Many computer programs have been developed for solving satisfiability problems which have
practical use. \newline In our discussion of the subject of algorithms in Chapter 3, we will discuss this
question further. In particular, we will explain the important role \textbf{the propositional satisfiability
problem plays in the study of the complexity of algorithms}
\end{tcolorbox}




