\documentclass{article}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[table,xcdraw]{xcolor}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{sidecap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{multirow}
\usepackage{standalone}
\usepackage[toc,page]{appendix}
\usepackage{listings}
\usepackage{a4wide}
\usepackage{pdfpages}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{mathtools}
\usepackage[normalem]{ulem}
\usepackage{arydshln}
\useunder{\uline}{\ul}{}
\usepackage[utf8]{inputenc}
\usepackage{relsize}
\usepackage{enumitem}
\usepackage{array}  % in your preamble
\usepackage[most]{tcolorbox}
\usepackage[table]{xcolor}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}

\title{Notes for Discrete Mathematics (2. Ed) by Rosen: Chapter 1: Logic and Proofs}
\author{Andreas Hansen}
\date{May 2025}

\begin{document}

\maketitle

\section*{\underline{Chapter 1.1: Propositional Logic} (pg. 1-13)}
\subsection*{Propositions: (pg. 2-3)}
\input{chp1_1_proplogic/props}

\newpage
\subsection*{Logic operator: Negation (pg. 3-4)}
\input{chp1_1_proplogic/neg}

\newpage
\subsection*{Logic operator (Connective): Conjuction (pg. 4)}
\input{chp1_1_proplogic/conj}

\newpage
\subsection*{Logic operator (Connective): Disjunction (pg. 4-5)}
\input{chp1_1_proplogic/disjunc}

\newpage
\subsection*{Logic operator (Connective): Exclusive or (XOR) (pg. 5-6)}
\input{chp1_1_proplogic/xor}

\newpage
\subsection*{Conditional Statements: (pg. 6-9)}
\input{chp1_1_proplogic/cond}
\subsection*{Biconditional Statements: (pg. 10)}
\input{chp1_1_proplogic/bicond}

\newpage
\subsection*{Truth Tables of Compound Propositions (pg. 11)}
\input{chp1_1_proplogic/comp_props}

\newpage
\subsection*{Logic and Bit Operations (pg. 12)}
\input{chp1_1_proplogic/log_bit}



\end{document}
