\subsubsection*{Exc 1.8: Suppose that Smartphone A has 256 MB RAM and
32 GB ROM, and the resolution of its camera is 8 MP;
Smartphone B has 288 MB RAM and 64 GB ROM, and
the resolution of its camera is 4 MP; and Smartphone C
has 128 MB RAM and 32 GB ROM, and the resolution
of its camera is 5 MP. Determine the truth value of each
of these propositions.}
\begin{enumerate}[label=(\alph*)]
\item Smartphone B has the most RAM of these three
smartphones.
\item Smartphone C has more ROM or a higher resolution
camera than Smartphone B
\item Smartphone B has more RAM, more ROM, and a
higher resolution camera than Smartphone A.
\item If Smartphone B has more RAM and more ROM than
Smartphone C, then it also has a higher resolution
camera
\item Smartphone A has more RAM than Smartphone B if
and only if Smartphone B has more RAM than Smartphone A.
\end{enumerate}
\subsubsection*{Solution:}
\\
\textbf{a):} True, because $288 \ \text{MB} > 256 \ \text{MB}$ (compared with Model A) and $288 \ \text{MB} > 128 \ \text{MB}$ (compared with Model C)
\\ \textbf{b):} True, because $5 \ \text{MP} > 4 \ \text{MP}$ and only one of the conditions needs to be met because of the word \textit{or}.
\\ \textbf{c):} False, because Smartphone B’s camera resolution (4 MP) is not higher than A’s (8 MP). Since this is a conjunction ('and'), all conditions must be true—but the camera comparison fails.
\\ \textbf{d):} False, because the hypothesis of this conditional statement is true and the conclusion is false.
\\ \textbf{e):} False, because the first part of this biconditional statement is false and the second part is true.
\\ This deals with a biconditinal statement, so we have:
$P = \text{Smartphone A has more RAM than Smartphone B}$
\\ $Q = \text{Smartphone B has more RAM than Smartphone A}$, then we have the bicondition:
\begin{equation*}
P \leftrightarrow Q \ \ , \ \ (\text{biconditional})
\end{equation*}
Check first statement $P$: $256 \ \text{MB} \not> 288 \ \text{MB}$ (compared with B), so A has NOT more ram and the first statement is false. \\
Check second statement $Q$: $288 \ \text{MB} > 256 \ \text{MB}$ (compared with A), so B has more RAM than A and the second statement is true.
